---
title: "AirIQ"
author: "Alexandre Verept"
date: "14/10/2019"
output: rmarkdown::github_document
---
# Visualizing datas from opendata with R
## Importing datas
```{r}
data=read.csv("https://opendata.lillemetropole.fr/explore/dataset/indice-qualite-de-lair/download/?format=csv&timezone=Europe/Berlin&use_labels_for_header=true", head=TRUE, sep=";")
```

## General view
```{r}
head(data)
summary(data)
```

## Data cleaning

We don't care about some of those informations such as Geo point, Geo shape...

```{r}
keeps = c("date_ech", "valeur")
data = data[keeps]
head(data)
```

Now we only have the data we want, so we will visualize it to have a better understanding (even if it's very basics datas)
```{r}
data$date_ech <- as.Date(data$date_ech, "%Y-%m-%d")
head(data)

dateRowData = data[data$date_ech >= "1970-01-01" & data$date_ech <= Sys.Date()+1,]

head(dateRowData)
```

```{r}
library(ggplot2)
qplot(data$valeur,
      geom="histogram",
      breaks=seq(1, 10, by = 1),
      binwidth = 1,
      fill=I("orange"), 
      col=I("red"),
      main = "Histogram of IQ values", 
      xlab = "Index",
      xlim=c(1,10))
```

We convert our weird date into a year/month/day

```{r}
data$date_ech <- as.Date(data$date_ech, "%Y-%m-%d")
head(data)
```

We will now see the IQ values by date

```{r}
ggplot(data = data, aes(x = date_ech, y = valeur))+
  geom_line(color = "orange", size = 0.5)
```

# Data from censors on the roof
## Importing datas

We take a look at 

```{r}
data2=read.csv("RecuperationDonnees.csv", head=TRUE, sep=";")
head(data2)
```

As previously we will show select informations that could be interesting. 

```{r}
keeps2 = c("TempExt", "HygroExt", "TempExt","PanneauS","Batterie","time")
data2 = data2[keeps2]
head(data2)
```


At first we convert the date and time:

```{r}
data2$time <- as.POSIXct(data2$time)
head(data2$time)
```

Some interesting graphs:

```{r}
ggplot(data = data2, aes(x = time, y = TempExt))+
  geom_line(color = "blue", size = 0.5)+ ggtitle("Temperature (degree celsius)")
```

```{r}
ggplot(data = data2, aes(x = time, y = HygroExt))+
  geom_line(color = "chartreuse3", size = 0.5)+ ggtitle("Humidity (%)")
```

```{r}
ggplot(data = data2, aes(x = time, y = PanneauS))+
  geom_line(color = "deeppink", size = 0.5)+ ggtitle("Sun exposure of the solar pannels (V)")
```

(Not very releavant)

```{r}
ggplot(data = data2, aes(x = time, y = Batterie))+
  geom_line(color = "darkorchid3", size = 0.5)+ ggtitle("Batterie level (A)")
```

(maybe releavant for the sun exposure)